GlobalSearchRegression.jl \\ \vspace{5mm} REPORT

### 2019-07-25 src/Output/decorations/latex/tpl.tex
cross validation latex output

@@

\begin{table}[!h]
  \centering
  \caption{Descriptive Statistics for the main dataset}
    \begin{tabular}{|p{2cm}|p{4cm}|c|c|c|c|c|c|}
    \hline
    Variable & Description & Obs. & Mean & Sd & Max & Min & \% Miss \\
    \hline
    \hline
    {{#descriptive}}{{^name}}
    \hline
    \end{tabular}
\end{table}

\begin{table}[!h]
  \centering
  \caption{Descriptive Statistics for the main dataset (cont.)}
    \begin{tabular}{|p{2cm}|p{4cm}|c|c|c|c|c|c|}
    \hline
    Variable & Description & Obs. & Mean & Sd & Max & Min & \% Miss \\
    \hline
    \hline
    {{/name}}{{#name}}{{name}} & Insert Description & {{nobs}} & {{mean}} & {{std}} & {{max}} & {{min}} & {{miss}}\% \\ 
    {{/name}}{{/descriptive}}\hline
    \end{tabular}
\end{table}
{{/input}}

@@

\begin{table}[!h]
    \centering
    \caption{Statistics}
    \begin{tabular}{|l|c|c|}
    \hline
    Variable {{name}} Statistics &  Coefficient Distribution &  T-test Distribution  \\
    \hline
    \hline
    Simple average    & {{b.avg}}      & {{t.avg}} \\
    \hline
    Median            & {{b.median}}   & {{t.median}} \\
    \hline
    Mode              & {{b.mode}}     & {{t.mode}} \\
    \hline
    Skewness          & {{b.std}}      & {{t.std}} \\
    \hline
    kurtosis          & {{b.skew}}     & {{t.skew}} \\
    \hline
    Positive Share    & {{b.kurt}}     & {{t.kurt}} \\
    \hline
    Significant Share & {{b.posshare}} & {{t.sigshare}} \\
    \hline
    \end{tabular}
\end{table}

@@

\begin{table}[!h]
  \centering
  \caption{K-fold cross-validation Results}
    \begin{tabular}{l c c}
    \hline
    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}}    \\
                    & {{kfolds}}-fold         & {{kfolds}}-fold \\
    Variables       & Mean                    & Median          \\
    \hline
    \hline
{{ median }}

--

{{ average }}

    {{#kfoldvars}}
      {{ varname }} & {{ meancoef }}{{stars}} & {{ mediancoef }}{{stars}} \\
                    & {{ meanstd }}           & {{ medianstd }}           \\
    {{/kfoldvars}}
    \hline

    Error out-sample &     &   \\
                     &     &   \\
    \hline
    \hline
    \multicolumn{3}{c}{\textit{Standard errors in parentheses}} \\
    \multicolumn{3}{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/crossvalidation}}

>>>>

\begin{table}[!h]
  \centering
  \caption{Descriptive Statistics for the main dataset}
    \begin{tabular}{|p{2cm}|c|c|c|c|c|c|c|}
    \hline
    Variable & Description & Obs. & Mean & Sd & Max & Min & \% Miss \\
    \hline
    \hline
    {{#descriptive}}{{^name}}
    \hline
    \end{tabular}
\end{table}

@@

\begin{table}[!h]
  \centering
  \caption{Descriptive Statistics for the main dataset (cont.)}
    \begin{tabular}{|p{2cm}|p{4cm}|c|c|c|c|c|c|}
    \hline
    Variable & Description & Obs. & Mean & Sd & Max & Min & \% Miss \\
    \hline
    \hline
    {{/name}}{{#name}}{{name}} &  & {{nobs}} & {{mean}} & {{std}} & {{max}} & {{min}} & {{miss}}\% \\ 
    {{/name}}{{/descriptive}}\hline
    \end{tabular}
\end{table}
{{/input}}

@@

\begin{table}[!h]
    \centering
    \caption{Statistics}
    \begin{tabular}{|l|c|c|}
    \hline
    Variable {{name}} Statistics &  Coefficient Distribution &  T-test Distribution  \\
    \hline
    \hline
    Simple average    & {{b.avg}}      & {{t.avg}} \\
    \hline
    Median            & {{b.median}}   & {{t.median}} \\
    \hline
    Mode              & {{b.mode}}     & {{t.mode}} \\
    \hline
    Std               & {{b.std}}      & {{t.std}} \\
    \hline
    Skewness          & {{b.skew}}     & {{t.skew}} \\
    \hline
    kurtosis          & {{b.kurt}}     & {{t.kurt}} \\
    \hline
    Positive Share    & {{posshare}} &  \\
    \hline
    Significant Share &  & {{sigshare}} \\
    \hline
    \end{tabular}
\end{table}

@@

\begin{table}[!h]
  \centering
  \caption{K-fold cross-validation Results}
    \begin{tabular}{l c c}
    \hline
    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}}                             \\
               &                  \multicolumn{2}{c}{ {{kfolds}}-fold }                  \\
    Variables  & Mean                             & Median                               \\
    \hline
    \hline
    {{#kfoldvars}}
    {{name}}   & {{#mean}}{{b}}{{stars}}{{/mean}} & {{#median}}{{b}}{{stars}}{{/median}} \\
               & {{#mean}}{{bstd}}{{/mean}}       & {{#median}}{{bstd}}{{/median}}       \\
    {{/kfoldvars}}
    \hline

    Error out-sample &  {{#outsample}}{{mean}}{{/outsample}}   & {{#outsample}}{{median}}{{/outsample}} \\
    \hline
    \hline
    \multicolumn{3}{c}{\textit{Standard errors in parentheses}} \\
    \multicolumn{3}{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/crossvalidation}}
